---
title: "R Project 1 - Hello R"
author: "Chelsea Cheung"
date: "9/16/2020"
output: 
  html_document: 
    fig_height: 10
    fig_width: 10
    highlight: textmate
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The data_saurus_dozen table has 1,846 rows and 3 columns. The variables included in the data frame are dataset (indicates which dataset the data are from), x (x-values), and y (y-values). 

### Exercise 2



Plotting the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in the dino dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in the star dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y for the dino dataset compared to the star dataset are both negative and the absolute difference between the two is 0.00151075 with the dino dataset having a larger negative number than the star dataset.

### Exercise 4

Plotting the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=3}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between 'x' and 'y' in the circle dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y for the dino dataset compared to the circle dataset are both negative and the absolute difference between the two is 0.00387151 with the circle dataset having a larger negative number than the dino dataset.

### Exercise 5

Plotting all the datasets in the datasaurus_dozen data frame:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

Calculating the correlation between 'x' and 'y' in all the datasets in the datasaurus_dozen data frame:

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```


